A unified model for parsing and sentence understanding

### 2016-03-13 writing/hard_stack_paper/paper.tex
More paper content.

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{5}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{Previous sentence encoder-based NN results}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{Our results}\\
\midrule
300d LSTM RNN encoders          & 1.7m                  & --                &   83.9      &   80.6       \\
\result{300d PINN-Ext w/o tracking}   
                        & ?                  & --                &   ?      &   81.9dv       \\
\result{300d PINN-Ext }
                        & ?                  & --                &   ?      &   \underline{84.8dv}       \\
\result{300d PINN }
                        & ?                  & 92.2+dv            &   ?    &   83.3+dv       \\          
% \result{300d PINN-Ext, sequence-based attn.   }     
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300d PINN-Ext, tree-based attn. }           
%                         & ?                  & --                &   ?      &   \textbf{?}\\
\midrule
\multicolumn{5}{c}{Other previous NN results}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \todo{[SB]: Estimate param counts as numbers come in.}} 
\end{table*}

@@

\todo{[JG,SB] Does anyone know of a better baseline TreeRNN implementation that we can use on Jagupard? We can use the CoreNLP SST model, but using a Java model as a baseline seems worrying unless we're guaranteed that it's competitively fast.}

Comparing model step time to the plain RNN of \citealt{li2015tree}. We use the small \citealt{pang2004sentimental} sentiment corpus that they use, and train with identical hyperparameters: ...

\todo{Comment on how long top-quality stand-alone greedy parsers take, for comparison.}

@@

\todo{Contrast sentence encoders w/ other models}

\result{Patterns in the examples that the tree model got right that the LSTM didn't}

@@

\begin{itemize}
\item It is possible to train a tree-structured model, without approximation, on large-scale language learning tasks.
\item Tree structure helps in large-scale language learning tasks. Not massively, but measurably.
\item An external parser is not necessary.
\end{itemize}

>>>>

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{5}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{Previous sentence encoder-based NN results}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{Our results}\\
\midrule
300d LSTM RNN encoders          & 1.7m                  & --                &   83.9      &   80.6       \\
\result{300d PINN-Ext-NoTracking}   
                        & ?                  & --                &   ?      &   81.9dv       \\
\result{300d PINN-Ext }
                        & ?                  & --                &   ?      &   \underline{84.8dv}       \\
\result{300d PINN }
                        & ?                  & 92.2+dv            &   ?    &   83.3+dv       \\          
% \result{300d PINN-Ext, sequence-based attn.   }     
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300d PINN-Ext, tree-based attn. }           
%                         & ?                  & --                &   ?      &   \textbf{?}\\
\midrule
\multicolumn{5}{c}{Other previous NN results}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \todo{[SB]: Estimate param counts as numbers come in.}} 
\end{table*}

@@

\todo{[JG] Write me!}

@@

\todo{[SB] Contrast sentence encoders w/ other models}

\result{[SB] Patterns in the examples that the tree model got right that the LSTM didn't}

@@

We find that:
\begin{itemize}
\item Our PINN-Ext-NoTracking model precisely implements tree-structured compositionality (as in a TreeLSTM), but is capable of exploiting batched computation for dramatic \todo{[JG] Numbers} improvements in inference speed.
\item While the use of tree-structure alone does not offer a substantial improvement over an LSTM baseline, our tree-sequence hybrid model (PINN-Ext) substantially outperforms that baseline, suggesting that our model is able to successfully exploit tree structure, while using sequential context information to better resolve ambiguity.
\item It is possible to remove the dependence on an external parser from our model ...
\end{itemize}
